---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{charger.manager}`

This package serves as a tool to inspect the potential installation sites
for electric vehicle chargers.

It:

* gathers data sources (chargers, infrastructure, population data)
* extracts, loads, and transforms these data
* visualizes the data (under construction)
* proposes additional charger potential for public and private stakeholders (under construction)

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install the development version of `{charger.manager}` like so:

```{r}
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
charger.manager::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```


